\begin{deluxetable*}{lcccc}
\tablecaption{Shared CHIME--DSA scattering index $\alpha$ from the uniform
single-exponential-PBF joint re-fit (prior $\alpha\in[1.0,6.0]$,
Section~\ref{sec:jointfit}), for co-detected sightlines whose joint fit constrains
$\alpha$ away from the prior bounds with acceptable per-band fit quality.
$\tau_{1\,\mathrm{GHz}}$ is the shared pulse-broadening time referred to
$1\,\mathrm{GHz}$; $C\times D$ is the number of temporal components modeled in the
CHIME and DSA-110 bands. Uncertainties are the $16$th/$84$th posterior
percentiles. Values are \emph{provisional-citable}; fixed-s² component counts are
adjudicated for the Tier-B sightlines (Section~\ref{sec:results-alpha}), and
population-level statistics remain qualitative pending FINAL figure regeneration.
Indices are predominantly sub-Kolmogorov ($\alpha<4$).
\label{tab:alpha}}
\tablehead{\colhead{Burst} & \colhead{$C\times D$} & \colhead{$\alpha$} &
  \colhead{$\tau_{1\,\mathrm{GHz}}$ [ms]} & \colhead{$\chi^2_\nu$ (C/D)}}
\startdata
FRB 20230814B\tablenotemark{a} & $2\times1$ & $1.53^{+0.09}_{-0.09}$ & $0.977^{+0.036}_{-0.033}$ & $1.04/1.27$ \\
FRB 20240229A & $1\times1$ & $2.40^{+0.01}_{-0.01}$ & $0.061^{+0.001}_{-0.001}$ & $1.41/0.99$ \\
FRB 20221203A\tablenotemark{b} & $1\times1$ & $2.56^{+0.04}_{-0.04}$ & $0.251^{+0.003}_{-0.003}$ & $1.14/4.55$ \\
FRB 20220506D & $2\times1$ & $2.66^{+0.16}_{-0.18}$ & $0.726^{+0.048}_{-0.050}$ & $1.04/1.16$ \\
FRB 20240203A & $1\times1$ & $3.28^{+0.04}_{-0.04}$ & $0.196^{+0.006}_{-0.005}$ & $1.14/1.16$ \\
FRB 20230307A & $3\times3$ & $3.32^{+0.06}_{-0.06}$ & $0.302^{+0.006}_{-0.007}$ & $1.02/1.34$ \\
FRB 20230325A & $1\times1$ & $4.35^{+0.04}_{-0.04}$ & $0.119^{+0.002}_{-0.002}$ & $1.30/1.03$ \\
FRB 20220310F\tablenotemark{c} & $2\times2$ & $5.1^{+0.2}_{-0.2}$ & $0.12^{+0.02}_{-0.02}$ & $1.1/1.5$ \\
\enddata
\tablenotetext{a}{Sub-Kolmogorov; well fit in both bands ($\chi^2_\nu=1.04,1.27$),
  so the shallow index is a measurement rather than a prior-rail artifact.}
\tablenotetext{b}{The elevated DSA-110 $\chi^2_\nu$ is a coherent shape misfit
localized at the bright pulse peak---off-peak residuals are white (RMS $\approx1$)
while the on-peak frequency-summed whitened residual reaches $\pm15\sigma$---where
a single exponentially-scattered component does not fully reproduce the DSA-110
pulse shape. The index is nonetheless robust to the intrinsic-width
parametrization: a per-band-$\zeta$ cross-fit gives a consistent
$\alpha=2.63^{+0.04}_{-0.04}$ with the same $\chi^2_\nu$, so $\alpha$ is stable but
is inferred through a model with residual structure at the peak.}
\tablenotetext{c}{Multiplicity exemplar: C2D2 all-exp fit after local re-prep
(Section~\ref{sec:results-alpha}, Figure~\ref{fig:whitney_mult}). Fixed-s²
evidence confirms the second DSA-110 component.}
\end{deluxetable*}
