\begin{deluxetable*}{lccccc}
\tablecaption{Turbulence spectral index $\beta$ from the uniform joint re-fit
(Section~\ref{sec:jointfit}), for co-detected sightlines whose joint fit constrains
$\beta$ away from the prior bounds with acceptable per-band fit quality. The
frequency-scaling index $\alpha=2\beta/(\beta-2)$ and the PBF shape are both
derived from $\beta$ at each likelihood evaluation. $\tau_{1\,\mathrm{GHz}}$ is the
shared pulse-broadening time referred to $1\,\mathrm{GHz}$; $C\times D$ is the
number of temporal components modeled in the CHIME and DSA-110 bands. The
Kolmogorov value is $\beta=11/3$ ($\alpha\approx4.4$); the square-law limit is
$\beta=4$ ($\alpha=4$, exponential PBF). Uncertainties are the $16$th/$84$th
posterior percentiles. Values are \emph{provisional-citable}; fixed-s² component
counts are adjudicated for the Tier-B sightlines
(Section~\ref{sec:results-alpha}), and population-level statistics remain
qualitative pending FINAL figure regeneration.
\label{tab:beta}}
\tablehead{\colhead{Burst} & \colhead{$C\times D$} & \colhead{$\beta$} &
  \colhead{$\alpha$ (derived)} & \colhead{$\tau_{1\,\mathrm{GHz}}$ [ms]} &
  \colhead{$\chi^2_\nu$ (C/D)}}
\startdata
% Values pending pipeline regeneration under the β-based co-model
% (Section~\ref{sec:jointfit}). Rows and component counts are preserved from the
% provisional-citable roster; β and derived α will be populated from a re-run of
% the dsa110-FLITS pipeline with the turbulence-spectrum likelihood.
\enddata
\tablenotetext{a}{Shallow frequency scaling; well fit in both bands, so the
measurement is a constraint rather than a prior-rail artifact.}
\tablenotetext{b}{The elevated DSA-110 $\chi^2_\nu$ is a coherent shape misfit
localized at the bright pulse peak---off-peak residuals are white (RMS $\approx1$)
while the on-peak frequency-summed whitened residual reaches $\pm15\sigma$---where
a single scattered component does not fully reproduce the DSA-110 pulse shape.
The turbulence index is nonetheless robust to the intrinsic-width
parametrization.}
\tablenotetext{c}{Multiplicity exemplar: C2D2 fit after local re-prep
(Section~\ref{sec:results-alpha}, Figure~\ref{fig:whitney_mult}). Fixed-s²
evidence confirms the second DSA-110 component.}
\end{deluxetable*}
