% Core methods section. The observed DM decomposes as
%   DM_obs = DM_MW,ISM + DM_MW,halo + <DM_cosmic>(z) + DM_intervening + DM_host,
% with DM_MW,ISM from NE2025 (NE2001/YMW16 retained as cross-checks), DM_MW,halo a 40 pc/cm^3 prior
% (Yamasaki & Totani 2020), <DM_cosmic>(z) the Macquart relation
% (Macquart et al. 2020; f_IGM=0.84, chi_e=0.875) for the point estimate; the
% forward-modeled cosmic term is drawn from the TNG-300 IGM log-normal
% (Walker et al. 2024) via the Connor et al. (2025) reproduction package,
% and DM_intervening a two-phase
% (hot mNFW + clumpy cool) CGM column for each intersecting foreground galaxy,
% reported raw and capped at b = 0.1 R_vir (the galaxy-interior regime).
%
% Scattering: measured tau_1GHz from nested-sampling fits (quality-gated on
% reduced chi^2, with R^2/normality informational only), compared against the
% predicted intervening tau from a thin-screen two-phase model.

\subsection{Dispersion Measure Decomposition}
\label{sec:dm}

The observed dispersion measure of each co-detection separates into Galactic,
cosmological, host, and (where the sightline intersects a foreground galaxy)
intervening contributions \citep{CordesChatterjee2019},
\begin{equation}
\mathrm{DM_{obs}} = \mathrm{DM_{MW}} + \langle\mathrm{DM_{cosmic}}\rangle(z)
+ \mathrm{DM_{int}} + \mathrm{DM_{host}},
\label{eq:dmbudget}
\end{equation}
Here $\mathrm{DM_{obs}}$ is the adopted CHIME phase-coherence measurement in
Table~\ref{tab:dm-measurements}, rather than the rounded discovery-catalog
value. This convention is used consistently in Table~\ref{tab:budget} and the
forward host-DM calculation. The Galactic term $\mathrm{DM_{MW}} = \mathrm{DM_{MW,ISM}} +
\mathrm{DM_{MW,halo}}$ split between disk and halo. We estimate the disk
contribution $\mathrm{DM_{MW,ISM}}$ from the NE2025 \citep{Ocker2026}
electron-density model integrated to $30\,\mathrm{kpc}$ (consistent with the
Galactic characterization of Section~\ref{sec:obs-mw}), with the older NE2001
\citep{CordesLazio2002} and YMW16 \citep{YMW2017} models retained as
cross-checks, and adopt a $\sim$40\,pc\,cm$^{-3}$ Milky-Way halo prior
\citep{YamasakiTotani2020}. The
cosmological mean $\langle\mathrm{DM_{cosmic}}\rangle(z)$ follows the Macquart
relation \citep{Macquart2020}. For the sightlines that cross a foreground
galaxy we model the intervening circumgalactic column $\mathrm{DM_{int}}$ as a
two-phase (hot modified-NFW plus clumpy cool) medium, taking the mNFW gas
profile from \citet{ProchaskaZheng2019}. Such intervening halos can add a
measurable DM contribution and, where the gas is turbulent, scattering on FRB
sightlines \citep{Ocker2021}, although an individual quiescent halo may instead
yield only an upper limit on its scattering contribution \citep{Prochaska2019}.

Rather than attribute the arithmetic residual of the mean-subtracted budget to
the host, we forward-model $\mathrm{DM_{host}}$ as a posterior. The diffuse
cosmic term is drawn as the intergalactic column
$\mathrm{DM_{IGM}}\sim\mathrm{LogNormal}(\mu(z),\sigma(z))$, with $\mu(z)$ and
$\sigma(z)$ the redshift-dependent parameters of the bivariate (IGM, halo)
log-normal fit to a mock FRB survey in IllustrisTNG-300 \citep{Walker2024},
adopted through the \citet{Connor2024} reproduction package and rescaled to the
IGM baryon fraction $f_{\rm IGM}=0.76^{+0.10}_{-0.11}$ that \citet{Connor2024}
infer from the DSA-110 sample. We use the IGM marginal rather than the total
cosmic column $\mathrm{DM_{cos}}=\mathrm{DM_{IGM}}+\mathrm{DM_X}$ because the
identified intervening halos ($\mathrm{DM_X}$) are already carried by our
separate $\mathrm{DM_{int}}$ census; adopting the total would double-count them.
This calibration replaces the earlier fixed-scaling
$\sigma_{\rm DM}=F\,z^{-1/2}$ form \citep{Macquart2020, McQuinn2014, James2022},
which \citet{Connor2024} show overstates the diffuse scatter because
$\sigma_{\rm DM}$ does not follow the $z^{-1/2}$ halo-Poisson scaling. The
Galactic-disk, Galactic-halo, and intervening columns are drawn from their own
priors (Appendix~\ref{app:host-forward-model}). We evaluate
$\mathrm{DM_{host}}=\mathrm{DM_{obs}}-\mathrm{DM_{MW}}-\mathrm{DM_{cosmic}}-
\mathrm{DM_{int}}$ per draw. Because $P(\mathrm{DM_{cosmic}})$ is right-skewed,
subtracting its \emph{mean}---as an arithmetic residual does---biases the
inferred host low; sampling the full distribution removes that bias and returns
an asymmetric posterior with a well-defined $P(\mathrm{DM_{host}}<0)$ per
sightline (Table~\ref{tab:budget}, Appendix~\ref{app:host-forward-model}).

\subsection{Intervening Foreground Galaxies and Clusters}
\label{sec:foreground}

The intervening term $\mathrm{DM_{int}}$ is sourced only where a sightline
actually crosses foreground circumgalactic or intracluster gas. We therefore
build $\mathrm{DM_{int}}$ from the confirmed foreground systems of the census
(Section~\ref{sec:obs-fg}, Table~\ref{tab:foreground}), and only from those
whose impact parameter places the sightline inside the gas. For galaxies we
require the sightline to pierce the virial radius ($b\le R_{\rm vir}$) and
integrate the column to the halo, capping the reported value at $b = 0.1\,R_{\rm
vir}$ to exclude the galaxy-interior regime. For clusters we require the
sightline to pass within $R_{500}$ ($b/R_{500}\le 1$), a conservative aperture
that across the whole sample selects a single cluster (FRB~20230307A,
J115120.4$+$714435 at $b/R_{500}=0.83$). The halo masses are the
per-candidate empirical estimates of the census (Section~\ref{sec:obs-fg}):
the vetted PS1/Legacy optical (and, where corroborated, WISE) stellar masses
converted through the \citet{Moster2013} stellar-to-halo-mass relation, so
the geometric census flags and the budget's intersection verdicts descend
from the same masses. Seven of the nine physical confirmed foreground galaxy
halos satisfy $b\le R_{\rm vir}$ and contribute: the single halos toward
FRB~20220310F and FRB~20240203A, two toward FRB~20240229A, and three of the
five toward FRB~20230307A, whose remaining two graze just outside their
virial radii ($b/R_{\rm vir}\approx1.3$--$1.4$), beyond the $R_{\rm vir}$
truncation of the modelled circumgalactic profile, and are excluded.
Refuted and inconclusive systems, and confirmed
systems whose sightline passes outside this aperture, do not contribute.

For each retained system we model the gas as a two-phase medium---a hot
modified-NFW component \citep{ProchaskaZheng2019} plus a clumpy cool
component---and integrate the electron column along the impact-parameter chord.
The cluster contribution uses the $M_{500}$ and $R_{500}$ of the
\citet{WenHan2024} catalog to fix the halo, computing the intracluster DM from
the modified-NFW profile at the sightline's impact parameter.
The $b\le R_{500}$ cut retains just the one cluster that pierces the halo; the
per-cluster DM columns for all four foreground clusters along the
FRB~20230307A sightline are shown in Figure~\ref{fig:clusters_icm}
(Appendix~\ref{app:clusters}).

\subsection{Scattering Attribution}
\label{sec:scattering}

We measure the pulse-broadening time and its frequency scaling from the
co-detected dynamic spectra and compare them against the scattering predicted
by each candidate screen. The candidate screens are the Milky-Way ISM, an
intervening circumgalactic medium, and a host galaxy, where the host can
dominate the scattering of a heavily broadened burst \citep{Ocker2022}. The fits are produced with a common
open-source reduction and fitting pipeline.

\subsubsection{The joint two-band fit}
\label{sec:jointfit}
\label{sec:beta-scattering-methods}

A single-band scattering fit cannot separate the scattering timescale from its
frequency scaling, because the pulse broadening
$\tau(\nu)=\tau_{1\,\mathrm{GHz}}\,(\nu/1\,\mathrm{GHz})^{-\alpha}$ enters a
single band only through its value at that band's frequency, so one band fixes
the product and not the slope. Co-detection breaks this degeneracy---the $\sim$1\,GHz
lever arm between CHIME/FRB ($\sim$0.4--0.8\,GHz) and DSA-110
($\sim$1.4\,GHz) measures the frequency scaling directly---but breaking the
degeneracy is not the same as measuring $\alpha$ in a physically consistent way.

The pulse-broadening function (PBF) shape and the scattering index $\alpha$ are
not independent observables. Both descend from the same turbulence spectrum. A
power-law electron-density fluctuation spectrum
$P_n(q)\propto q^{-\beta}$ produces a phase structure function
$D_\phi(\rho)\propto\rho^{\beta-2}$, whose Fourier transform determines the
angular brightness distribution and hence the PBF shape, while the diffractive
scale and Fresnel arguments give the frequency scaling
$\tau\propto\nu^{-2\beta/(\beta-2)}$ for a thin screen---i.e.\
$\alpha=2\beta/(\beta-2)$ \citep{Rickett1990, Cordes2025}. The common
one-sided exponential PBF,
$p_E(t,\tau)=\tau^{-1}e^{-t/\tau}\,\Theta(t)$, corresponds to a square-law
structure function $D_\phi(\rho)\propto\rho^2$ ($\beta=4$); within the same
thin-screen mapping its delay scales as $\tau\propto\nu^{-4}$. A Kolmogorov
spectrum ($\beta=11/3$) instead yields a
power-law PBF tail $p_d(t)\propto t^{-\beta/2}$ and $\alpha\approx4.4$
\citep{Cordes2025}.

Because $\beta$ determines both the PBF shape and $\alpha$, they must be
co-modeled. Choosing a fixed PBF family and freely varying $\alpha$ inside it
is physically inconsistent, because the exponential PBF assumes square-law
statistics, which already imply $\alpha\approx4$. If the true medium is
Kolmogorov---or anything other than square-law---fitting an exponential PBF
will absorb the shape mismatch into a biased $\alpha$ \citep{Cordes2025}.

We therefore replace the phenomenological pair $(\tau_{1\,\mathrm{GHz}},\alpha)$
with the turbulence spectral index $\beta$ as the fundamental parameter. For
each $\beta$ in the fit, the PBF shape is computed directly from the
corresponding phase structure function $D_\phi(\rho)\propto\rho^{\beta-2}$, and
the frequency scaling index follows as $\alpha=2\beta/(\beta-2)$ under the
thin-screen assumption. The free parameters of the joint fit are
$(\tau_{1\,\mathrm{GHz}},\beta)$ and the per-telescope pulse parameters
(arrival time $t_0$, intrinsic width $\zeta$, and a residual DM offset
$\delta\mathrm{DM}$). The fit operates on the CHIME/FRB and DSA-110 dynamic
spectra simultaneously, with the PBF shape and $\alpha$ both derived from
$\beta$ at every likelihood evaluation rather than chosen independently.

Under this model, the Kolmogorov member $\beta=11/3$ ($\alpha\approx4.4$) and
the square-law/exponential endpoint $\beta=4$ are specific points in the
physically allowed thin-screen inertial-range mapping. Because
$\alpha=2\beta/(\beta-2)$ decreases as $\beta$ increases in this regime, a
formally shallow empirical scaling is not interpreted by itself as a turbulence
spectral index; it instead indicates that the assumed scattering family, burst
morphology, or inertial-range closure is incomplete.

The square-law endpoint requires a further caution, which we build into the
results rather than append as a caveat. When the diffractive scale drops below
the turbulence inner scale, the phase structure function becomes locally
quadratic and $\alpha\to4$ regardless of the underlying spectral index. An
inner-scale-dominated medium and a genuine $\beta=4$ spectrum are therefore
observationally degenerate \citep{Cordes2016, Cordes2025}. A posterior that
concentrates at $\beta=4$ is consequently \emph{not} reported as a measurement
of square-law turbulence; it instead marks the closure regime in which the
thin-screen inertial-range mapping no longer determines $\beta$. To make this
explicit, the per-sightline results table (Section~\ref{sec:results-alpha})
carries a closure-regime label alongside each entry: \texttt{inertial} for a
resolved $\beta$ within the inertial range, and \texttt{endpoint-degenerate}
for the square-law / inner-scale endpoint. This ensures that no square-law
endpoint is read as an inertial-range spectral index. Geometry family (thin vs
extended) is recorded separately and is not folded into this label.

Concretely, the model dynamic spectrum in each band is built per frequency
channel as an intrinsic Gaussian profile of width $\zeta$ convolved with the
$\beta$-derived PBF. In the square-law limit $\beta\to4$ the convolution is
evaluated with the closed-form Gaussian--exponential expression in a
numerically stable scaled-complementary-error-function form; below that limit
it is evaluated with the power-law-tail PBF implied by the phase structure
function, whose asymptotic decay is $t^{-\beta/2}$. The residual
dispersion-measure offset $\delta\mathrm{DM}$ shifts the per-channel arrival
time by the $\nu^{-2}$ cold-plasma delay relative to the band reference
frequency and contributes intra-channel dispersion smearing: the dispersive
sweep across one native channel of width $\Delta\nu_{\rm ch}$,
$\Delta t_{\rm DM} \approx 8.3\,\mu\mathrm{s}\,
(\mathrm{DM}/\mathrm{pc\,cm^{-3}})\,(\Delta\nu_{\rm ch}/\mathrm{MHz})\,
(\nu/\mathrm{GHz})^{-3}$ \citep{LorimerKramer2004}, enters the model as a
boxcar of that duration, represented by its variance-matched Gaussian
($\sigma_{\rm DM}=\Delta t_{\rm DM}/\sqrt{12}$) added in quadrature to
$\zeta$. Each spectrum is fit at its instrument-optimized dedispersion DM
(Section~\ref{sec:data}), so $\delta\mathrm{DM}$ is a small per-band residual
about that reference rather than a re-measurement of the total DM, and the
smearing term is evaluated at the offset from each product's de-smeared
baseline: for coherently dedispersed products only the fitted residual
$|\delta\mathrm{DM}|$ contributes, while for incoherently dedispersed
products the full dedispersion DM plus residual sets the smearing at the
native channel width.

The two bands enter the fit as independent datasets sharing
$(\tau_{1\,\mathrm{GHz}},\beta)$. Within a band, channels are treated as
independent Gaussian measurements: the per-channel noise standard deviation
is estimated from off-pulse samples of the same spectrum with the
median-absolute-deviation estimator scaled to Gaussian equivalence, which is
robust to residual burst power and narrowband interference. Channels flagged
by the upstream masking, dead channels, and channels with vanishing
off-pulse variance are excluded from the likelihood through a per-channel
validity mask rather than interpolated.

\subsubsection{Sub-band validation of the frequency scaling}
\label{sec:subband}
\label{sec:beta-subband}

The frequency scaling recovered by the joint fit can be validated independently
of the PBF parametrization by fitting the scattering time directly in frequency
sub-bands. We split each band into sub-bands (four across CHIME, three across
DSA-110), collapse each to a one-dimensional profile, and fit a scattered
pulse---a Gaussian intrinsic shape convolved with a one-sided exponential tail,
the exponentially-modified Gaussian---to each sub-band independently, leaving the
scattering time $\tau$ free at every frequency. Because each $\tau_i$ is measured
per sub-band with no power law imposed, the slope of $\tau_i(\nu_i)$ is an
estimate of the frequency scaling that shares neither parametrization nor
likelihood with the joint two-dimensional fit.

This cross-check is a slope diagnostic, not an independent turbulence
measurement, and we treat it as such for a specific reason. Each sub-band $\tau_i$
is itself fit with an exponential (EMG) kernel---the $\beta=4$ family the joint
fit is designed to avoid privileging---so each $\tau_i$ inherits a shape-mismatch
bias wherever the true PBF is not exponential. The sub-band \emph{slope} is
informative only insofar as that bias is common to all sub-bands and cancels in
the ratio; it does not cancel when the mismatch is frequency-dependent, which is
the generic case (the fraction of the pulse in the power-law tail, and hence the
bias on a per-band exponential $\tau_i$, itself varies with frequency). We
therefore report the sub-band slope as a validation diagnostic---a consistency
check on the joint-fit frequency scaling---and never as a measurement of the
turbulence spectral index. The sub-band validation figure and event-level
sub-band comparisons are presented with the scattering analysis
(Section~\ref{sec:results-alpha}).

% TODO(methods-subband-validation): Restore a sub-band validation artifact only
% after fit re-validation. The restored figure should state the included bursts,
% exclusion reasons, fit family, and whether the sub-band slopes are used as a
% validation diagnostic or as physical turbulence constraints.
% Figure float lives in Section~\ref{sec:results-alpha} as PLACEHOLDER
% fig:subband_tau_validation (wishlist W4); D3: diagnostic only.

\subsubsection{Gain-marginalized likelihood}
\label{sec:gainmarg}
\label{sec:beta-gainmarg}

The per-channel amplitude of an FRB spectrum is unknown and strongly modulated
by scintillation; carried as a free spectral envelope it leaves correlated
structure in the fit residuals and invalidates a $\chi^2$ goodness-of-fit test.
We therefore marginalize the per-channel gain analytically. With a Gaussian
prior on the gain the per-channel evidence is available in closed form (a
matched-filter likelihood), and the recovered gain absorbs both the burst
spectrum and the scintillation pattern. This removes the spectral and
scintillation structure from the residual, so that the reduced $\chi^2$ and the
lag-1 residual autocorrelation become meaningful quality gates, and it lowers
the sampled dimensionality.

Because the marginalization deliberately absorbs the scintillation pattern into
the gain, the scattering fit does not measure scintillation. The
decorrelation-bandwidth products used later
(Section~\ref{sec:results-scintillation}) come from a separate
autocorrelation-function analysis path applied to the same dynamic spectra, not
from this likelihood. The one interaction to guard against is at low
signal-to-noise, where a fully free per-channel gain can absorb genuine
scattering-induced spectral smearing into the spectral envelope and thereby bias
the scattering time low; we therefore keep the gain prior informative (finite
width) rather than flat, and verify on the final fits that the
$\tau_{1\,\mathrm{GHz}}$ posterior is stable against the gain-prior width before
quoting any low-$\tau$ result. The gain prior is a per-channel zero-mean
Gaussian of variance $s^2$; unless stated otherwise $s^2$ is profiled at its
maximum-marginal-likelihood value, and it is held fixed whenever Bayesian
evidences are compared across likelihood variants
(Section~\ref{sec:multicomp}), so that evidence differences reflect the
temporal model rather than the gain hyperparameter.

The priors on the sampled parameters are deliberately simple and, except for
one anchor, independent of the initialization, as evidence-based model
comparison requires. $\tau_{1\,\mathrm{GHz}}$ and each intrinsic width
$\zeta$ are log-uniform over $10^{-4}$--$10^{3}$\,ms. $\beta$ is uniform over
the thin-screen inertial branch, by default $3\le\beta\le4$, the image of
$4\le\alpha\le6$ under $\alpha=2\beta/(\beta-2)$. Each per-band
$\delta\mathrm{DM}$ is uniform over $\pm50\,\mathrm{pc\,cm^{-3}}$ about the
dedispersion reference; bounding the residual keeps a broad, heavily
smeared solution from escaping into an unphysically large
$|\delta\mathrm{DM}|$ degeneracy. Each arrival time $t_0$ is uniform in
a window anchored on that band's profile-peak estimate, the only
data-derived quantity in the prior.

We sample the posterior by nested
sampling \citep{Skilling2004}, as implemented in \texttt{dynesty}
\citep{Speagle2020}, using random-walk sampling with at least 600 live
points (at least 800 for the higher-dimensional multi-component variants)
and terminating when the estimated remaining log-evidence falls below 0.5.
Parameter summaries are posterior-weighted percentiles, and the $\alpha$
posterior is derived deterministically from the $\beta$ samples. Each fit is
quality-gated on two criteria: the reduced $\chi^2$ of its noise-whitened,
gain-marginalized residuals (accepted in $0.3\le\chi^2_\mathrm{red}\le1.5$,
rejected above 10, and flagged for individual inspection between---or
suspiciously below 0.3), and the absence of lag-one residual
autocorrelation (Durbin--Watson statistic within 1--3). $R^2$ and
residual normality are treated as informational.

\subsubsection{Multiple temporal components}
\label{sec:multicomp}
\label{sec:beta-multicomp}

Some bursts comprise more than one temporal sub-component, a common feature of
the resolved FRB population \citep{Hessels2019, Pleunis2021}. An unmodeled
second component is partially absorbed by a single scattered pulse---as a steeper
frequency scaling and a larger scattering time---and so biases the inferred
$\beta$, distorting both the fitted PBF shape and $\alpha$ simultaneously. We
extend the likelihood to $N$ temporal components per band, each contributing its
own $(t_0,\zeta)$ while $(\tau_{1\,\mathrm{GHz}},\beta)$ remain shared across
both bands and all components, and we select the number of components per band
by Bayesian evidence subject to a residual check. Because the evidence
normalization differs between
likelihood variants, the component counts are compared on a single matched grid
in which even the one-component model is evaluated through the multi-component
likelihood, with the gain-prior variance held fixed across counts
(Section~\ref{sec:gainmarg}), so that evidence differences are meaningful.
Component arrival times
within a band are ordered and separated by a data-derived minimum spacing,
keeping the fit identifiable at every prior sample.

The evidence comparison is not by itself the final acceptance gate. For each
candidate multiplicity we inspect the two-dimensional data, best-fit model, and
whitened residual dynamic spectra in both bands. A component choice is rejected
and re-fit if coherent burst power remains in the residuals, or if the collapsed
profiles show a resolved sub-component that is absent from the model, even when
the scalar goodness-of-fit statistics are otherwise acceptable. This visual and
residual audit is part of the component-selection procedure, in which a fit with
missed sub-components is treated as diagnostic and re-fit at higher multiplicity
until it passes the same check. A clean single-component co-detection in our sample,
for which the joint fit returns a well-constrained $\beta$ with white residuals,
validates the method; accepted multi-component cases will be presented in
Section~\ref{sec:results-alpha}.
