\section{Conclusions}
\label{sec:conclusions}

We draw conclusions here for the association tests, the foreground census, and
the dispersion-measure budget decomposition; conclusions on the scattering fits, the
scintillation products, the turbulence parameters, and the burst energies follow
in the corresponding sections.

\begin{itemize}
\item \textit{Association.} All twelve candidate pairs are genuine
co-detections: each has a chance-coincidence probability $P_{\rm cc}<10^{-6}$
under deliberately conservative windows chosen to maximize the estimated
chance rate, a timing residual consistent with
the inter-site geometric delay, and a positionally consistent localization.
The pre-specified association statistic included a DM-agreement term for eight
events; the other four retain the more conservative position-and-time-only
probability with $f_{\rm DM}=1$. Independently of that association calculation,
the new phase-coherence analysis constrains CHIME/FRB and DSA-110 DMs for all
twelve events, with a maximum band difference of
$0.117\,\mathrm{pc\,cm^{-3}}$; the narrower CHIME/FRB fits are adopted.

\item \textit{Foreground census.} The FRB~20230307A sightline is the only one in
the twelve-burst sample that passes within $R_{500}$ of a foreground cluster,
contributing an intracluster column of order $180\,\mathrm{pc\,cm^{-3}}$
($\approx80$--$330\,\mathrm{pc\,cm^{-3}}$---a factor of $\sim$4---across
the profile choice and the cluster-parameter systematics, the mass capped
by the cluster's ROSAT non-detection).
The intervening contribution to the
dispersion-measure budget is dominated by that sightline, with a secondary
circumgalactic contribution toward FRB~20240229A and small columns on the
two other sightlines with confirmed foreground systems;
the contributing foreground galaxies lie in the outer circumgalactic medium
($b/R_{\rm vir}\approx0.46$--$0.96$ under vetted empirical masses), with
individual columns of $\approx6$--$76\,\mathrm{pc\,cm^{-3}}$. The census
reaches only as deep as the wide-field
catalogs available at this declination, so a sightline without a confirmed
intervening system is unconstrained by survey depth, not demonstrably free of
foreground gas.

\item \textit{Dispersion-measure budget.} With $\mathrm{DM_{host}}$ forward-modeled as a
posterior rather than an arithmetic residual, the decomposition is consistent,
within the uncertainties, with the host supplying a minority of the
extragalactic column on every redshift-constrained sightline (median
$\mathrm{DM_{host}}$ from $\approx-10$ to $+170\,\mathrm{pc\,cm^{-3}}$, with
broad cosmology-dominated uncertainties): the extragalactic column is
typically dominated by the cosmological term, not the host. This attribution
inherits the adopted IGM baryon-fraction normalization
($f_{\rm IGM}=0.76$), itself inferred partly from DSA-110 sightlines
(Section~\ref{sec:dm}). The intervening term is dominated by the
cluster-crossing sightline, and the one marginally negative host median
(FRB~20220310F, $z=0.48$, $P(\mathrm{DM_{host}}<0)\approx0.5$) reflects
scatter about the diffuse cosmic
normalization rather than an unphysical host; the highest-redshift sightline
(FRB~20230814B, using the provisional internal value $z=0.55$) is likewise
consistent with zero host.
Sightlines without spectroscopic
host redshifts are excluded from all distance-dependent statements.
\end{itemize}

The two-screen analysis remains pending: the required fixed-index
consistency refits of the scattering time ($\alpha$ fixed to 4) do not yet
exist, and
the free-$\alpha$ joint-fit values cannot be paired with the DSA bandwidths
for this purpose. No screen verdict,
screen distance, or medium attribution is claimed. Cross-matching the
provisional fitted-scattering values with the foreground census singles
out FRB~20230307A as the only accepted-fit sightline with a non-negligible
fiducial foreground contribution (about 22\%); this is a plausible partial
contribution, not a causal identification. The remaining comparison is limited
by imaging coverage, inconclusive foreground redshifts, or unusable propagation
fits.

% TODO(conclusions): Add the remaining bullets as their analyses clear
% re-validation, ordered by evidential dependency:
% 4. trusted scattering-fit and scintillation constraints;
% 5. trusted event-by-event screen interpretation;
% 6. trusted turbulence or morphology statements;
% 7. trusted energy measurements.
%
% Avoid quoting retired counts, budget residuals, host-dominated fractions, beta
% or alpha values, scintillation-excess factors, event attributions, or burst
% energies until the corresponding Results slot is repopulated.
