\section{Discussion}
\label{sec:discussion}

The per-sightline budget lets us ask, for each burst, whether its scattering can
be assigned to a specific screen. The clearest evidence for an extragalactic
screen is the diffractive-scintillation excess of Section~\ref{sec:scattering}:
on the mid-latitude sightlines where the Galactic floor is reliable, the measured
diffractive bandwidth lies $\sim$7--11$\times$ below the NE2025 prediction, and
never above it, so the dominant scattering screen is not the Milky Way. For the
prototype FRB~20221203A the three separated scintillation scales
(Figure~\ref{fig:scint_screens})---a Galactic floor far above and a
pulse-broadening screen far below the resolved diffractive scale---localize that
screen to the host or an intervening medium rather than the Galaxy.

Whether that screen is intervening or intrinsic to the host is, in principle,
decided by the foreground census. The two sightlines that pierce a foreground
galaxy's interior (FRB~20220310F, FRB~20230307A) carry both the
largest predicted intervening dispersion and the largest predicted intervening
pulse-broadening (Figure~\ref{fig:budget}, right), and are the natural candidates
for an intervening scattering screen. The high-amplitude scintillation-excess
sightlines, however, are not in general the galaxy-interior ones, so the present
evidence favors a host-dominated screen for the strongly scattered bursts, with
an intervening screen remaining viable only where a confirmed foreground galaxy
lies at small impact parameter. Discriminating the two requires the
measured-versus-predicted $\tau$ comparison that Figure~\ref{fig:budget} sets up
but cannot yet close until the per-sightline $\tau$ set is finalized into the
overlay; this is the test we identify as the principal remaining measurement for
the sample.

\subsection{Burst multiplicity as a systematic on the turbulence spectrum}
\label{sec:disc-alpha}

The result of Section~\ref{sec:results-alpha} is a cautionary systematic for any
single-component fit to the turbulence spectrum. A temporal sub-component omitted
from the model is partially absorbed into the scattering tail and biases
$\beta$---classically toward steeper values, as a larger scattering time and
steeper frequency scaling mimic the unmodeled flux, but the bias can instead rail
the fit against a prior bound when the multiplicity is split across the two bands,
as in FRB~20220310F where an unmodeled DSA-110 sub-pulse drives $\beta$ to a
prior rail. Because $\beta$ determines both the PBF shape and the frequency
scaling, an unrecognized companion distorts the entire scattering model
simultaneously rather than shifting a single index. We verified that a favored
second component is not an artifact of the likelihood: its evidence gain is flat
across the gain-prior scale (so it is not prior-driven), reconstructing the
single-component residual reproduces the whiteness statistic that flagged the
burst, and the companion sits well inside the resolvable separation.

The $\beta$-based fit removes the PBF as an independent systematic, because the
PBF shape and the frequency scaling are both derived from the same $\beta$ at
each likelihood evaluation. A sightline whose posterior is consistent with
$\beta=4$ is consistent with square-law statistics and an exponential PBF, while
the Kolmogorov point is $\beta=11/3$ with $\alpha\approx4.4$. In the thin-screen
inertial-range mapping, $\alpha=2\beta/(\beta-2)$ decreases as $\beta$ increases,
bottoming out at $\alpha=4$ in the $\beta\to4$ square-law limit, and steeper
spectra ($\beta\ge4$) remain pinned at $\alpha=4$; the closure therefore admits
no $\alpha<4$ at all (Section~\ref{sec:beta-scattering-methods};
Appendix~\ref{app:emg-alpha4}). A formally shallow empirical scaling
($\alpha<4$) consequently cannot be read as a
shallower-than-Kolmogorov turbulence spectrum under any parameter choice; it
instead indicates that the
assumed scattering family, burst morphology, or inertial-range closure is
incomplete. For the marginal sightlines---those whose posterior rails or reaches
a prior bound---we quote no turbulence index, treating them as unconstrained
rather than anomalous.
