\section{Introduction}
\label{sec:intro}

Fast radio bursts \citep[FRBs;][]{Lorimer2007, Thornton2013} provide compact,
bright backlights through ionized gas on Galactic, circumgalactic,
intergalactic, and host-galaxy scales. Their dispersion measures trace the
integrated electron column---anchoring the cosmological Macquart relation
\citep{Macquart2020}---while pulse broadening and diffractive scintillation
respond to turbulent structure and screen geometry
\citep[e.g.,][]{CordesChatterjee2019}. Individual sightlines have already
demonstrated the reach of these propagation diagnostics: scattering and
scintillation together can localize a screen to circumburst plasma
\citep{Masui2015}, limit the turbulent column of an intervening galaxy halo
\citep{Prochaska2019, Ocker2021}, or implicate the host interstellar medium as
the dominant scattering site \citep{Ocker2022}. At the population level, the
first CHIME/FRB catalog established that scattering times at 600\,MHz span
several orders of magnitude and are in tension with Galactic-only or IGM-only
origins \citep{CHIME2021Catalog, Chawla2022}. Yet jointly interpreting these
observables for any one burst remains degenerate: a given dispersion measure
can be distributed among multiple media, and a given scattering time can be
produced by different screen locations and turbulence spectra.

Co-detections by CHIME/FRB and DSA-110 help break these degeneracies by
measuring the same burst over a wide frequency baseline. CHIME/FRB samples
low frequencies at 400--800~MHz, where dispersion delays and scattering are
larger, while DSA-110 observes near 1.4~GHz, where the same event is less
broadened. A single-band measurement constrains only the scattering time at
that band's frequency. The $\sim$1\,GHz lever arm of a co-detection, by
contrast, constrains the frequency scaling of arrival-time structure and pulse
broadening directly, which no single dataset provides alone. A co-detection
also introduces a critical association step: the two detections must be
demonstrated to be the same astrophysical burst before their
dispersion-measure and scattering information can be combined.

This paper is organized around that joint interpretation. We first establish
that the twelve candidate pairs are genuine co-detections and measure a
per-telescope dispersion measure for each (Section~\ref{sec:obs}). We then
build the sightline-by-sightline context those measurements require: the
Galactic foreground expected along each line of sight, a redshift-validated
census of the intervening galaxies and clusters, and a forward-modeled
decomposition of each dispersion measure into its Galactic, cosmological,
intervening, and host terms (Sections~\ref{sec:obs}--\ref{sec:results}). The
association tests, the foreground census, and the dispersion-measure budget
are reported in full. The scattering, scintillation, turbulence, and
energetics analyses are presented with their validation status stated
explicitly: quantities that have not yet passed independent verification are
identified as provisional wherever they appear, and every claim built on them
is bounded accordingly.
