\section{Methods}
\label{sec:methods}

This section defines how the co-detections are associated, how the
dispersion-measure and scattering budgets are modeled, and how the fitted
quantities used in Section~\ref{sec:results} are validated.

\input{sections/toa.tex}
\input{sections/budget.tex}

\subsection{Band-restricted burst energies}
\label{sec:methods-energies}

For each sightline with a spectroscopic host redshift and a well-constrained
per-band amplitude fit, we estimate the isotropic-equivalent burst energy directly
from the joint CHIME--DSA fit, without extrapolating either band's spectrum
beyond where it is constrained.
The fit returns a per-band spectral amplitude and index,
$F_X(\nu) = c_{0,X}\,(\nu/\nu_{\mathrm{ref},X})^{\gamma_X}$, which we place on
an absolute scale with each telescope's per-channel radiometer conversion
$\sigma_{S,X}(\nu) = \mathrm{SEFD}_X(\nu)\,/\,[\sqrt{n_{\mathrm{pol}}\,\Delta\nu\,\Delta t}\,G_X(\nu)]$,
taking the system-equivalent flux density and primary-beam gain $G_X$ from the
DSA-110 \citep{Law2024} and CHIME/FRB \citep{CHIMEFRB2018,Michilli2021} flux
scales. We integrate over each instrument's observing band---CHIME over
$0.400$--$0.800\,\mathrm{GHz}$ and DSA over $1.311$--$1.499\,\mathrm{GHz}$,
\begin{equation}
E_{\mathrm{iso}} = \frac{4\pi D_L^2(z)}{1+z}\left[
  \int_{\nu_1^{C}}^{\nu_2^{C}} s_C\,F_{\mathrm{CHIME}}(\nu)\,d\nu
  + \int_{\nu_1^{D}}^{\nu_2^{D}} s_D\,F_{\mathrm{DSA}}(\nu)\,d\nu
\right],
\label{eq:eiso}
\end{equation}
with $D_L(z)$ from the fiducial \textit{Planck}\,2018 cosmology
\citep{Planck2018}, the $(1+z)$ bandwidth k-correction applied, and
$1\,\mathrm{Jy\,ms\,Hz} = 10^{-29}\,\mathrm{J\,m^{-2}}$. This band-restricted
integral constrains the energy released within the observed spectral envelope:
it avoids the large, model-dependent extrapolation that a single power-law fit
across the full $0.4$--$1.5\,\mathrm{GHz}$ span would require, at the cost of not
counting flux in the unobserved $0.8$--$1.3\,\mathrm{GHz}$ gap.

Two properties of this definition must be stated prominently. First, the
observed bands map to \emph{per-burst} rest-frame intervals: CHIME's
$0.400$--$0.800\,\mathrm{GHz}$ samples the rest-frame band
$[0.400(1+z),\,0.800(1+z)]\,\mathrm{GHz}$ and DSA's
$1.311$--$1.499\,\mathrm{GHz}$ samples $[1.311(1+z),\,1.499(1+z)]\,\mathrm{GHz}$,
so the rest-frame window shifts from burst to burst. These band-restricted
energies are therefore \emph{not} comparable to literature energies computed
over a fixed rest-frame band, and cannot be placed on a standard FRB luminosity
function without a spectral-model extrapolation that we deliberately avoid here;
we report them as observed-band quantities only. Second, the single $(1+z)$ in
Eq.~\ref{eq:eiso} is the bandwidth (time-dilation) k-correction, which is common
to both bands; the differing per-band spectral indices $\gamma_C,\gamma_D$ enter
only the in-band flux integrals $\int F_X(\nu)\,d\nu$, not the k-correction, so
the two-band sum is internally consistent despite the single $(1+z)$ factor.
% TODO(energies-fixed-band-variant): Optional under V3 — if luminosity-function
% comparison is needed, elect a fixed rest-frame-band companion E_iso (define
% the band, extrapolation across the 0.8--1.3 GHz gap, and table column), then
% restore a Methods sentence. D5 lock (2026-07-10) dropped the unconditional
% promise; see docs/rse/specs/decision-d2-d5-scattering-design-locks.md.
Energy rows are deferred until the spectral
amplitudes, calibration path, host-redshift provenance, and inclusion rule are
ready to be described and cited in the manuscript.
