\section{Observations and Sample}
\label{sec:obs}

The working sample is the set of candidate fast-radio-burst co-detections seen
by CHIME/FRB \citep{CHIMEFRB2018} at $0.4$--$0.8$\,GHz and by DSA-110
\citep{Law2024} at $\sim$1.4\,GHz between 2022 February and 2024 February. The
defining asset of the sample is that each candidate event is observed across a
wide frequency baseline, which---as developed in Section~\ref{sec:jointfit}---can
separate scattering time from frequency scaling more strongly than a single-band
fit once the association and per-telescope dispersion-measure provenance are
re-validated. The per-burst designations, epochs, DMs, timing residuals, and
chance-coincidence probabilities are withheld in this draft pending the V6
association and DM-observation re-validation pass.

\subsection{Dynamic spectra and reduction}
\label{sec:data}

For each co-detection we analyze a pair of total-intensity dynamic spectra---one
per facility---derived from the CHIME/FRB and DSA-110 baseband recordings
(24 spectra in total; provenance and array geometry in
\texttt{DATA\_SOURCES.md} of the companion \texttt{dsa110-FLITS} archive). Each
spectrum is loaded with its frequency axis standardized to ascending order and
its per-channel bandpass normalized, so the fitted amplitudes are free of the
band-edge rolloff. All fits, quality gates, and figures in this paper are
produced by the open \texttt{dsa110-FLITS} pipeline (\texttt{pipeline/}), which
we reference throughout for reproducibility. We do not catalog the fine
baseband morphology of each burst here; the only morphological distinction the
analysis depends on---whether a burst resolves into more than one temporal
component---is treated where it matters, in the multi-component fit of
Section~\ref{sec:multicomp}.

\subsection{Scattering fits}
\label{sec:obs-scatt}

The Methods section defines the joint two-band model, the $\beta$-based
scattering closure, the temporal multiplicity treatment, and the quality gates
used to decide which per-sightline quantities are citable
(Sections~\ref{sec:jointfit} and~\ref{sec:multicomp}). Scattering-fit results
are withheld until the fit re-validation ladder has restored trust in the
underlying burst-data fits.

% TODO(obs-scattering): Reinsert any joint-fit montage only after the fit
% products shown in the figure have passed the re-validation contract.

\subsection{Foreground-galaxy search}
\label{sec:obs-fg}

To establish which sightlines could carry an intervening dispersion or
scattering contribution, the analysis must first identify candidate foreground
galaxies and clusters, assign redshift provenance, and decide whether each
candidate is foreground, background, or inconclusive. The catalog search,
verdict logic, impact parameters, halo-mass proxies, and any derived
foreground table are withheld until the foreground-census re-validation ladder
has restored trust in those products.

% TODO(obs-foreground): Restore this subsection after the foreground census has
% passed re-validation. The restored text should state the candidate list, the
% redshift provenance, the foreground/background/inconclusive verdict logic, and
% the per-section burst list without quoting revoked candidate counts.
