\section{Results}
\label{sec:results}

The association tests, the foreground census, and the dispersion-budget
decomposition are reported below. The scattering fits for individual sightlines,
the scintillation products, the turbulence parameters, the burst energies, and
the measured-versus-predicted scattering comparison are presented in the
following subsections as they are finalized.

\FloatBarrier
\subsection{Association of the co-detections}
\label{sec:results-association}

All twelve candidate pairs pass the association tests of
Section~\ref{sec:toa}. Under the conservative, chance-maximizing windows of
Section~\ref{sec:toa-pcc}, every pair has a chance-coincidence probability
$P_{\rm cc}<10^{-8}$---fewer than one in a hundred million such pairings would be
expected to arise by chance---and passes the positional-coincidence check; the
timing residuals, referenced to
400\,MHz under the shared DSA-DM convention, are consistent with the
predicted inter-site geometric delay (Table~\ref{tab:sample}). The eight
bursts with constrained CHIME-side dispersion measures also pass the
CHIME--DSA DM-agreement check; the remaining four are retained as
position-and-timing associations, since their CHIME sub-band fits do not
provide a constraining independent DM. We therefore treat all twelve pairs as
genuine co-detections in what follows.

\FloatBarrier
\subsection{Per-sightline dispersion budget}
\label{sec:results-budget}
\label{sec:budget}

Table~\ref{tab:budget} reports the decomposition of Eq.~\ref{eq:dmbudget}
along the twelve sightlines. Three features organize the sample. First, the
intervening term is strongly concentrated: summed over the confirmed
foreground systems of Section~\ref{sec:obs-fg}, $\mathrm{DM_{int}}$ exceeds
$100\,\mathrm{pc\,cm^{-3}}$ on only one sightline (FRB~20230307A,
$241\,\mathrm{pc\,cm^{-3}}$, dominated by the intracluster column of
Section~\ref{sec:dominant-systems}), while the remaining sightlines carry
$\lesssim 85\,\mathrm{pc\,cm^{-3}}$ and four tabulate
$\mathrm{DM_{int}}=0$---for two distinct reasons. FRB~20220506D and
FRB~20240122A lie outside the deep-imaging footprints, so their sightlines
are constrained only by the shallow all-sky layers and their intervening
terms are unconstrained rather than measured to be zero (note~u). FRB~20240203A
and FRB~20240229A carry confirmed foreground halos, but those halos lie
beyond the virial radii implied by their assumed masses, so the modeled
columns vanish; their zeros are conditional on the mass assumption (note~m),
and FRB~20240203A is additionally outside the deep footprints. One sightline
(FRB~20230814B) crosses a foreground halo in the
galaxy-interior regime ($b \approx 4.6$\,kpc), where the reported column is
capped at its $b=0.1\,R_{\rm vir}$ value rather than extrapolated through the
core. Second, the forward-modeled host posteriors
(Section~\ref{sec:dm}, Appendix~\ref{app:host-forward-model}) are broad and
asymmetric, dominated by the cosmological scatter: their medians span
$\mathrm{DM_{host}}\approx10$--$210\,\mathrm{pc\,cm^{-3}}$, the largest on
FRB~20240229A ($211^{+46}_{-112}\,\mathrm{pc\,cm^{-3}}$), and every sightline is
consistent with a host contributing a minority of the extragalactic column once
the width of the cosmological term is folded in. Third, the two
highest-redshift sightlines (FRB~20220310F, FRB~20221203A), whose
mean-subtracted point residuals were negative, have host posteriors consistent
with zero ($P(\mathrm{DM_{host}}<0)\approx0.45$; Table~\ref{tab:budget}); those
negative point values reflected the skew of $P(\mathrm{DM_{cosmic}}\,|\,z)$ at
these redshifts, not an unphysical host. The three sightlines without
spectroscopic host redshifts are excluded from all distance-dependent terms
(Table~\ref{tab:budget}, note p).

The predicted intervening pulse broadening from the thin-screen two-phase
model is small everywhere: $\tau_{\mathrm{int}} \le 0.024$\,ms at 1\,GHz,
with the largest values on the sightlines whose confirmed halos are crossed
at the smallest impact parameters. The comparison of these predictions with
the measured scattering times is deferred until the joint fits pass
re-validation.

% TODO(results-budget-scattering): Restore the measured-vs-predicted
% scattering comparison (fig:budget overlay, tau_obs column) only after the
% V1 fit ladder clears.

\input{budget_table}

\subsubsection{Dominant intervening systems}
\label{sec:dominant-systems}

Of the twelve sightlines, only one crosses a foreground cluster within its
characteristic radius. The FRB~20230307A sightline passes at $b/R_{500}=0.83$
from the \citet{WenHan2024} cluster J115120.4$+$714435 ($z=0.200$,
$\log M_{500}=14.1$), for which the two-phase modified-NFW model predicts an
intracluster column of order $160\,\mathrm{pc\,cm^{-3}}$
(Figure~\ref{fig:clusters_icm}). This column is uncertain at the factor-of-two
level: an X-ray/SZ-motivated isothermal $\beta$-model with the same $M_{500}$
and a cosmic gas fraction gives a somewhat higher central value
($\approx250\,\mathrm{pc\,cm^{-3}}$), and propagating the richness-based
$M_{500}$ ($\sim\!0.2$\,dex scatter), the gas fraction ($f_{\rm gas}=0.10$--$0.16$),
and the profile shape spans $\approx100$--$560\,\mathrm{pc\,cm^{-3}}$
(Appendix~\ref{app:host-forward-model}). The mNFW profile is calibrated on
$\sim\!L_\star$ halos \citep{ProchaskaZheng2019} and is not guaranteed to hold at
$\log M_{500}=14.1$; its value sits near the low end of the $\beta$-model range
and should be read as a conservative estimate. This is nonetheless the single
dominant intervening system in the sample. The other foreground clusters recovered along this and the two
other cluster-bearing sightlines all lie beyond $R_{500}$, where the modeled
column drops steeply; they are excluded from the budget even where the profile
remains formally nonzero, and none approaches the FRB~20230307A cluster in
predicted contribution.

The confirmed foreground galaxies lie at impact parameters of tens to a few
hundred kpc, in the outer circumgalactic medium rather than the galaxy interior.
Each therefore adds only a small dispersion, and no single galaxy halo dominates
its sightline's intervening column.
The intervening dispersion in this sample is thus concentrated almost entirely on
the one cluster-crossing sightline and is small on the rest; the sightlines
carrying no confirmed within-aperture system are limited by survey depth
(Section~\ref{sec:obs-fg}), not shown to be free of foreground gas.

\FloatBarrier
\subsection{Scintillation and screen attribution}
\label{sec:results-scintillation}

% TODO(results-scintillation): Insert after the scintillation products and
% scattering fits are re-run under the re-validation contract. This subsection
% should connect the decorrelation-bandwidth measurements, single-screen tests,
% and screen-attribution claims only after both ingredients are trusted.
%
% Required before filling:
% - Re-run DSA-band scintillation products under the validation contract.
% - Complete CHIME-band scintillation campaign where needed.
% - Re-establish the scattering fits used in any tau * Delta-nu product.
% - Decide whether scintillation acts as a geometry-selection constraint or as
%   part of a fitted two-screen model.
%
% Candidate future artifact, once trusted:
% - fig:scint_screens

\FloatBarrier
\subsection{Turbulence spectrum and burst multiplicity}
\label{sec:results-alpha}

% TODO(results-turbulence): Insert only after the joint scattering fits pass
% the fit re-validation ladder and the geometry-selection campaign has decided
% which model family is citable per sightline. Do not quote rail classes,
% alpha=4 limits, class fractions, median beta, or campaign-era fit values as
% sky results.
%
% This slot should eventually report:
% - the validated per-sightline turbulence parameters, if any;
% - the model family under which each value is citable;
% - multiplicity decisions that survive re-validation;
% - any morphology-induced bias demonstration that is re-established.
%
% Candidate future artifacts, once trusted:
% - tab:beta
% - fig:whitney_mult

The component-multiplicity audit is already informative as a validation step,
even before the turbulence parameters are restored as citable measurements.
Figure~\ref{fig:jointmodel-pair-whitney} shows the current FRB~20220310F
(\textit{whitney}) two-dimensional data/model/residual panel after the CHIME
side is forced to retain its resolved second pulse. The full set of eleven
current joint-model morphology-audit panels is included in
Appendix~\ref{app:jointmodel-pairs}. We use these figures to check whether the
adopted component count leaves coherent burst power in the residuals; we do not
yet quote the fitted scattering or turbulence parameters from them.

\FloatBarrier
\subsection{Band-restricted burst energies}
\label{sec:burst-energies}

% TODO(results-energies): Insert only after the energy re-validation pass.
% A citable row requires a trusted host redshift, trusted per-band spectral
% amplitudes, a checked calibration path, and a resolved inclusion rule.
%
% Required before filling:
% - Re-establish c0 and gamma values from trusted fits or an energy-specific
%   trusted export.
% - Resolve any prior-rail or selection-rule issues.
% - State the burst list and exclusion reasons explicitly.
%
% Candidate future artifact, once trusted:
% - tab:burst-energies
