\subsection{Time-of-Arrival Crossmatching}
\label{sec:toa}

Before attributing the dispersion-measure and scattering budgets we verify that the
twelve events are genuine co-detections---the same burst seen by both
facilities, with arrival times consistent under the cold-plasma dispersion law
and the geometric light-travel delay between the sites. The wide baseline
between CHIME/FRB (400--800\,MHz) and DSA-110 ($\sim$1.4\,GHz) makes the
co-detections a test of the $1/\nu^2$ dispersion scaling and of the relative
timing alignment of the two facilities \citep{Lorimer2007, Thornton2013}.

\subsubsection{Delay model}

We translate the arrival times at the two central frequencies to a common
reference frequency $\nu_{\mathrm{ref}}=400$\,MHz. The cold-plasma dispersion
delay is
\begin{equation}
\Delta t_p = K_{\mathrm{DM}}\,\mathrm{DM}
\left(\frac{1}{\nu_{\mathrm{ref}}^2}-\frac{1}{\nu_{\mathrm{obs}}^2}\right),
\label{eq:dmdelay}
\end{equation}
with $K_{\mathrm{DM}} = 4.148808\times10^{3}\,\mathrm{MHz^2\,pc^{-1}\,cm^3\,s}$.
The geometric light-travel difference between the observatories is
\begin{equation}
\tau_{\mathrm{geo}} = \frac{(\mathbf{p}_2-\mathbf{p}_1)\cdot\hat{\mathbf{s}}}{c},
\label{eq:geodelay}
\end{equation}
where $\mathbf{p}_1$ and $\mathbf{p}_2$ are the GCRS position vectors of CHIME
and DSA-110, respectively, and $\hat{\mathbf{s}}$ is the unit vector from Earth
toward the source. With this ordering, $\tau_{\rm geo}$ predicts
$t_{\rm CHIME}-t_{\rm DSA}$ because the radiation propagates along
$-\hat{\mathbf{s}}$. The timing residual is the difference between the
frequency-corrected CHIME-minus-DSA offset and the predicted geometric delay; a
residual of zero indicates perfect agreement.

\subsubsection{Chance-coincidence probability}
\label{sec:toa-pcc}

A small timing residual shows that a CHIME and a DSA trigger are \emph{consistent}
with being the same burst; it does not by itself show that they \emph{are}. The
complementary question is how often an \emph{unrelated} CHIME burst would fall
close enough to a given DSA burst---in arrival time, sky position, and dispersion
measure simultaneously---to mimic the association by chance. We quantify this with
a chance-coincidence (false-alarm) probability $P_{\rm cc}$.

We model unrelated CHIME bursts as a Poisson point process on the sky. For DSA
burst $i$, the expected number of unrelated CHIME bursts that land inside the joint
association window is
\begin{equation}
\mu_i = R \,\Omega_{\rm win}\, (2\,\Delta t)\, f_{\rm DM}(\mathrm{DM}_i,\Delta\mathrm{DM}),
\label{eq:pcc_mu}
\end{equation}
where $R$ is the all-sky CHIME burst rate (per unit solid angle per unit time),
$\Omega_{\rm win}$ is the sky area of the positional window, $2\,\Delta t$ is the
full arrival-time window (a $\pm\Delta t$ coincidence gate), and
$f_{\rm DM}(\mathrm{DM}_i,\Delta\mathrm{DM})$ is the fraction of the CHIME DM
distribution lying within $\pm\Delta\mathrm{DM}$ of the burst's DM---the factor
that additionally requires a chance interloper to match in DM, not only in
time and position. For such a rare-event Poisson process the probability that
\emph{at least one} unrelated burst falls in the window is
\begin{equation}
P_{{\rm cc},i} = 1 - e^{-\mu_i} \simeq \mu_i \qquad (\mu_i \ll 1),
\label{eq:pcc_p}
\end{equation}
so $P_{\rm cc}$ is, to excellent approximation, just the expected number of chance
matches.

Equation~\eqref{eq:pcc_mu} conditions on a single DSA burst, so the sample-level
false-alarm expectation is the sum $\sum_j \mu_j$ over the \emph{trial set}: the
complete list of DSA-110 triggers searched for a CHIME/FRB counterpart over the
2022~February--2024~February overlap, not merely the twelve that matched. The
look-elsewhere penalty is therefore carried explicitly by that sum. Under the
chance-maximizing windows below, the eight pairs whose pre-specified
association statistic included a DM constraint have
$\mu_j\sim2$--$6\times10^{-9}$, while the four position-and-time-only pairs use
$f_{\rm DM}=1$ and have $\mu_j=4.4\times10^{-7}$. The twelve reported pairs sum
to $\sum_i\mu_i\approx1.8\times10^{-6}$. Even the conservative extension to the
entire 64-burst DSA-110 trial set, obtained by scaling by the searched-to-matched
ratio $64/12$, remains below $10^{-5}$ and leaves the conclusion unchanged.

We evaluate Eq.~\eqref{eq:pcc_mu} with deliberately conservative,
chance-\emph{maximizing} inputs, so the reported $P_{\rm cc}$ is an upper bound on
the true false-alarm rate: an all-sky CHIME rate rounded up to
$R = 10^{3}\,\mathrm{sky^{-1}\,day^{-1}}$ (above the Catalog~1 value of
$\simeq525\,\mathrm{sky^{-1}\,day^{-1}}$; \citealt{CHIME2021Catalog}), a
$0.5^{\circ}$-radius positional disk ($\Omega_{\rm win}=0.785\,\mathrm{deg^2}$),
$\Delta t = \pm1\,\mathrm{s}$, and $\Delta\mathrm{DM}=\pm5\,\mathrm{pc\,cm^{-3}}$.
These windows are far wider than the actual per-event tolerances (millisecond
timing, arcsecond-scale DSA localization, and the measured DM agreement), so using
each event's true tolerances can only lower $P_{\rm cc}$. As an independent check,
a direct Monte-Carlo of the background point process reproduces the closed-form
$P_{\rm cc}$ to $0.3\%$ in a regime where both are measurable, and the result is
stable across several orders of magnitude of variation in each window and in $R$.

\subsubsection{Residuals and systematics}

Table~\ref{tab:sample} summarizes the association diagnostics. The tabulated
residuals use the shared DSA-DM convention: the CHIME and DSA arrivals are both
referenced to 400\,MHz with the DSA catalog DM, so the residual is a
timing/geometry consistency check rather than an independent per-telescope-DM
comparison. Re-referencing the CHIME arrivals with their independently measured
DMs would inject millisecond-scale shifts for the largest CHIME--DSA DM offsets,
so those shifts are tracked separately rather than folded into the association
residual.

We adopt the sign convention $\Delta t = \Delta t_{\rm inter\text{-}site} -
\tau_{\rm geo}$, where $\Delta t_{\rm inter\text{-}site}$ is the CHIME-minus-DSA
arrival offset after both are referenced to 400\,MHz (Eq.~\ref{eq:dmdelay}) and
$\tau_{\rm geo}$ is the predicted geometric delay (Eq.~\ref{eq:geodelay}); a
positive residual means the CHIME arrival is later than the shared-DM geometric
prediction relative to DSA, and $\Delta t=0$ is exact agreement. The geometric
term is itself bounded: for the $1345\,\mathrm{km}$ CHIME (DRAO)--DSA-110 (OVRO)
baseline, $|\tau_{\rm geo}| \le |\mathbf{p}_2-\mathbf{p}_1|/c \approx 4.5\,$ms for
any source direction. For the twelve source directions here,
$\tau_{\rm geo}=-2.30$ to $-2.03\,$ms: the wavefront reaches CHIME first and
DSA-110 $2.03$--$2.30\,$ms later. The residual is therefore not error-free but carries a
per-burst systematic of order the inter-site clock/timestamp alignment
($\sigma_{\rm clock}\sim1$\,ms) plus, for the eight originally DM-conditioned
pairs, the residual dispersive delay left by the CHIME--DSA DM offset. With the
new phase-coherence measurements, the largest band offset is
$0.117\,\mathrm{pc\,cm^{-3}}$ (FRB~20221113A), corresponding to approximately
$2.8$\,ms when re-referenced between 1.5\,GHz and 400\,MHz,
a convention-dependent term reported separately rather than folded in. We
assign each pair a $1\sigma$ timing budget $\sigma_i$ by combining, in
quadrature, the shared-DM combined CHIME+DSA arrival error, the intrinsic pulse
width, and the $\sigma_{\rm clock}\sim1$\,ms term, and accept a pair when its
residual is consistent with the geometric delay to within $|\Delta t_i| \le
3\sigma_i$. The budget is dominated by the pulse width for the two broadest
bursts, so the largest raw residual---$+8.4$\,ms for FRB~20220506D, a $74$\,ms-wide
burst---is only $0.1\sigma$. All twelve residuals ($-2.7$ to $+8.4$\,ms,
tabulated with their $\sigma_i$ in Table~\ref{tab:sample}) satisfy the criterion;
the tightest is FRB~20221203A at $2.6\sigma$. A residual of several tens of ms
for a narrow, well-localized burst---inconsistent with both its few-ms budget and
the $\lesssim\!4.5$\,ms geometric delay---would fail. We stress
that the association verdict does not rest on the timing residual alone: the
decisive gates are the chance-coincidence probability, positional coincidence,
and (for the eight bursts with a pre-specified DM-conditioned association
term) DM agreement, for which the residual is a
supporting consistency diagnostic.

Evaluated with the conservative windows above, the eight originally
DM-conditioned bursts
have $P_{\rm cc}<10^{-8}$ individually, while each of the four conservatively
classified pairs has the deliberately less selective position-and-time-only
value $P_{\rm cc}=4.4\times10^{-7}$. Thus all twelve have $P_{\rm cc}<10^{-6}$,
and their sample-summed expectation is $\sum_i\mu_i\approx1.8\times10^{-6}$.
Because these class-aware estimates remain far below unity, the
chance-coincidence test establishes the co-detections; positional coincidence
and the independently measured phase-coherence DMs provide additional checks.
All twelve pass the positional-coincidence check and now have constrained
CHIME and DSA phase-coherence measurements (Table~\ref{tab:dm-measurements}).
The four pairs marked `assoc.~(pos.)' in Table~\ref{tab:sample} retain that
label because their pre-specified association calculation used position and
timing alone; we do not apply a post-selection DM factor. For those four we set
$f_{\rm DM}=1$ in
Eq.~\eqref{eq:pcc_mu}---the DM criterion is not imposed, so their
$P_{\rm cc}$ is a time-and-position bound only, consistent with the
position-only verdict; the eight originally DM-conditioned bursts carry the full
$f_{\rm DM}(\mathrm{DM}_i,\Delta\mathrm{DM})<1$ factor. The reported
$P_{\rm cc}$ values are thus computed per association class, and the
position-only $P_{\rm cc}$ are, if anything, conservative relative to the
originally DM-conditioned ones.

The per-burst DM provenance (per-telescope DM, method, and CHIME--DSA agreement)
is given in Table~\ref{tab:dm-measurements} and in the accompanying
machine-readable catalog; the intermediate association diagnostics are
provided in the archival data release (Section~\ref{sec:data-availability});
Table~\ref{tab:sample} carries the manuscript-facing timing residual, $P_{\rm cc}$,
and association-verdict columns. Across the twelve phase-coherence fits,
$\mathrm{DM_{CHIME}}-\mathrm{DM_{DSA}}$ has mean
$+0.013\,\mathrm{pc\,cm^{-3}}$ and maximum absolute value
$0.117\,\mathrm{pc\,cm^{-3}}$; no coherent $\sim0.4\,\mathrm{pc\,cm^{-3}}$
instrument offset remains.
